IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-08 paper/retrofit.tex
Minor edits
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

Here are two more examples of language features which have an
interesting interpretation when viewed in the setting of multiple tasks.

@@

When considering tasks, we will instead say that the allocation of a new
stack frame with a raised label corresponds to the creation of a new
isolated task; a sample encoding using our language is shown in
Figure~\ref{fig:toLabeled}.
However, this is not enough: in a stack discipline, one generally
expects stack entries to be processed in order, rather than in parallel
as would be suggested by isolated tasks.  The sequential processing of
the task queue corresponds to a specific \emph{scheduling policy} of
these tasks.  The recasting of the problem to one of scheduling
highlights the essential difference between termination-insensitive and
termination-sensitive non-interference, and we will show how different
scheduling policies give different security guarantees.

\paragraph{Exceptions versus message passing}
Another language feature that has caused difficulty for
many information flow control systems is exceptions handling,
when built on top of this stack discipline.
%
The key difficulty appears when considering the propagation of exceptions
across stack boundaries where the current label is restored.
%
If the exception crosses this boundary, it can leak information about the
inner secret computation into a public computation; hence, one must
explicitly ensure that |toLabeled| does not propagate exceptions.

>>>>

Here are two more examples of language features which have an
interesting interpretation when interpreted as task communication.

@@

When considering tasks, we will instead say that the allocation of a new
stack frame with a raised label corresponds to the creation of a new
isolated task; a sample encoding using our language is shown in
Figure~\ref{fig:toLabeled}.
There is one more ingredient: in a stack discipline, one generally
expects stack entries to be processed in order, rather than in parallel
as would be suggested by isolated tasks.  The sequential processing of
the task queue corresponds to a specific \emph{scheduling policy} of
these tasks.  In fact, the choice of scheduling here is the essential difference that
determines whether or not one can prove termination-insensitive or
termination-sensitive non-interference. We will show how different
scheduling policies give different security guarantees.

\paragraph{Exceptions versus message passing}
Another language feature that has caused difficulty for
many information flow control systems is exception handling
when built on top of this stack discipline.
%
The key difficulty appears when considering the propagation of exceptions
across stack boundaries where the current label is restored.
%
If the exception crosses this boundary, it can leak information about the
inner secret computation into a public computation; hence, one must
explicitly ensure that |toLabeled| does not propagate exceptions.
